Standardized crypto-loans on\\ the Cardano blockchain

### 2021-02-04 papers/actus2021/article.tex
minor changes

\documentclass[runningheads]{llncs}
\usepackage[latin9]{inputenc}
\usepackage{url}[obeyspaces]
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[unicode=true,
 bookmarks=false,
 breaklinks=false,pdfborder={0 0 1},backref=section,colorlinks=false]
 {hyperref}

@@

\begin{verbatim}
if condition 
	then 
		perform\_something1()
		continue() 
	else 
		perform\_something2() 
		continue()
\end{verbatim}
\noindent
Translating this to Marlowe would inline contents of \texttt{continue()} twice and, given that ACTUS
contracts are essentially generated using continuation as an accumulator,
this would lead to exponential explosion of the size of any ACTUS
contract that has conditionals in their state transition logic.

@@

Using static analysis for Marlowe~\cite{} it is possible fully to check a particular contract instead of using random
sampling. That would allow some refinements: 
\begin{itemize}
\item More balanced sampling: the space of contract terms depends linearly on
the coverage, e.g. if we cover 10\% of all possible contract terms
- we'll cover 10\% of all contracts. Different contracts have different
sets of risk factors, and so different search spaces. For instance, a
contract with 3 risk factors (e.g. 3 observations of an interest rate)
would span over $n^3$ values while a contract with 10 risk
factors would span over $n^{10}$. Meanwhile, the space of
all risk factors in all contracts doesn't linearly depend on the coverage.
% SJT explain last sentence. 
\item Dependency tracking: an SMT-solver is potentially likely to be more aware of execution
paths that lead to the failure of a test, a feature that could significantly reduce
search space. 
\item Completeness: if not timed out, SMT-solving is decidable while sampling
is semi-decidable. 
\end{itemize}

>>>>

\documentclass[runningheads]{llncs}
\usepackage[latin9]{inputenc}
\usepackage{url}[obeyspaces]
\usepackage{amsmath}
\usepackage{alltt}
\usepackage{graphicx}
\usepackage[unicode=true,
 bookmarks=false,
 breaklinks=false,pdfborder={0 0 1},backref=section,colorlinks=false]
 {hyperref}

@@

\begin{alltt}
if condition 
  then 
    perform\_something1()
    continue() 
  else 
    perform\_something2() 
    continue()
\end{alltt}
\noindent
Translating this to Marlowe would inline contents of \texttt{continue()} twice and, given that ACTUS
contracts are essentially generated using continuation as an accumulator,
this would lead to exponential explosion of the size of any ACTUS
contract that has conditionals in their state transition logic.

@@

Using static analysis for Marlowe~\cite{marlowe-efficient} it is possible fully to check a particular contract instead of using random
sampling. That would allow some refinements: 
\begin{itemize}
\item More balanced sampling: the space of contract terms depends linearly on
the coverage, e.g. if we cover 10\% of all possible contract terms
- we'll cover 10\% of all contracts. Different contracts have different
sets of risk factors, and so different search spaces. For instance, a
contract with 3 risk factors (e.g. 3 observations of an interest rate)
would span over $n^3$ values while a contract with 10 risk
factors would span over $n^{10}$. Meanwhile, the space of
all risk factors in all contracts doesn't linearly depend on the coverage.
% SJT explain last sentence. 
\item Dependency tracking: an SMT-solver is potentially likely to be more aware of execution
paths that lead to the failure of a test, a feature that could significantly reduce
search space. 
\item Completeness: if not timed out, SMT-solving is decidable while sampling
is semi-decidable. 
\end{itemize}
